---
title: "Advanced water cost model"
author: "Xiangyu Liu"
date: "2018/3/29"
output: html_document
---

I added the water table depth data into 'awwadata.csv' and rerun the water cost model.
```{r}
library(dplyr)
awwa2<- read.csv("awwadata2.csv")

```

##deal with the independent and dependent variables
```{r}

awwa2$costs<-gsub(",","",awwa2$ISBeforeDepreciation)%>%as.numeric()
awwa2$SurfaceMG<-awwa2$Surface*awwa2$AnnualMGallonsSoldTotal/100
awwa2$GroundMG<-awwa2$Ground*awwa2$AnnualMGallonsSoldTotal/100
awwa2$PurchasesMG<-awwa2$Purchases*awwa2$AnnualMGallonsSoldTotal/100
```

##run the fixed effect model
```{r}
library(plm)
zz <- plm(costs ~ SurfaceMG + GroundMG + PurchasesMG, data = awwa2,model="pooling")
zz <- plm(costs ~ SurfaceMG + GroundMG + PurchasesMG + depth, data = awwa2, model = "between")
summary(zz)

```


##run the quantile regression model
```{r}
library(quantreg)
Qreg50=rq(awwa2$costs~awwa2$SurfaceMG+awwa2$GroundMG+awwa2$PurchasesMG+awwa2$depth, tau=0.50)
summary(Qreg50)
```

##add depth * GroundMG
```{r}
awwa2$depthGroundMG<-awwa2$depth*awwa2$GroundMG
zz <- plm(costs ~ SurfaceMG + GroundMG + PurchasesMG + depthGroundMG, data = awwa2, model = "between")
summary(zz)
```

The 'depth * GroundMG' variable is still not significant... 
 
 
## only for the gw part
```{r}
awwa3<-awwa2[awwa2$Ground == 100.000,]
zz <- plm(costs ~ GroundMG + depth, data = awwa3, model = "between")
summary(zz)
```

For the regression model only for the gw part, the depth variable is significant!

## only for the gw part(depth*GroundMG)
```{r}
zz <- plm(costs ~ depthGroundMG, data = awwa3, model = "between")
summary(zz)
```

## only for the gw part(depth + GroundMG + depth*GroundMG)

```{r}
zz <- plm(costs ~ depth+GroundMG + depthGroundMG, data = awwa3, model = "between")
summary(zz)
```

##cost/GroundMG(unit) ~ depth
```{r}
##calculate the unit
awwa3$unitcost<-awwa3$cost/awwa3$GroundMG

##delete the Inf row
d<-awwa3[c(1:4,6:43),]

zz <- plm(unitcost ~ depth, data = d, model = "between")

summary(zz)
```

## % of gw in relation to depth to groundwater 
```{r}
awwa2$percentofgw <- awwa2$Ground /(awwa2$Ground+awwa2$Surface)
zz <- plm(percentofgw ~ depth, data = awwa2, model = "between")
summary(zz)
```

Here we can find that when a facility decide to use groundwater or surface water, the depth to groundwater has a significant influence.
